Fleet Definitions

### 2021-02-26 docs/GBFleetDefinitions.Rmd
added author, date to GBfleet rmd

---
title: "Fleet Definitions"
output:
  bookdown::html_document2:
    code_fold: hide
    number_sections: false
csl: apa-annotated-bibliography.csl
bibliography: references.bib
link-citations: yes
---

@@

```
```{r dendro1,out.width="100%",fig.cap="The denrogram obtained from a nearest-neighbor, hierarchical cluster analysi on all gears used in the Georges Bank Ecological Production unit defined by Statistical areas"}
knitr::include_graphics("figures/dendrogram1.png")
```

>>>>

---
title: "Fleet Definitions"
author: Andy Beet
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    code_fold: hide
    number_sections: false
csl: apa-annotated-bibliography.csl
bibliography: references.bib
link-citations: yes
---

@@

```
```{r dendro1,out.width="100%",fig.cap="The denrogram obtained from a nearest-neighbor, hierarchical cluster analysis on all gears used in the Georges Bank Ecological Production unit defined by statistical areas"}
knitr::include_graphics("figures/dendrogram1.png")
```
